---
title: "Manual21005"
author: "Jinhao Zhao"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manual21005}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Overview

__StatComp21005__ is a simple R package developed for simple linear fitting of independent and dependent variables. Two functions are _Gradient_Descent_ and _Stochastic_GD_.

## _Gradient_Descent_

The running time of _Gradient_Descent_ is short, but the result may fall into local minimum.
The source R code is as follows:

```{r}
Gradient_Descent<-function(x,y,learning_rate){
  x0=rep(1,length(x))
  x_data=cbind(x0,x) 
  y_data=matrix(y,length(y),1)
  theta=matrix(c(1,1),2,1)
  diff=x_data%*%theta-y_data 
  gradient=(1/length(x))*(t(x_data)%*%diff)
  while (!((abs(gradient[1,1])<0.0001)&(abs(gradient[2,1])<0.0001))) {
    theta=theta-learning_rate*gradient
    diff=x_data%*%theta-y_data 
    gradient=(1/length(x))*(t(x_data)%*%diff)
  }
  func=paste('y=',theta[1,1],'+',theta[2,1],'x')
  return (func)
}
```

## Introduction about _Stochastic_GD_

The running time of _Stochastic_GD_ may be long, but the result is unlikely to fall into a local minimum. 
The source R code is as follows:

```{r}
Stochastic_GD<-function(x,y,learning_rate){
  x0=rep(1,length(x))
  x_data=cbind(x0,x)
  y_data=matrix(y,length(y),1)
  theta=matrix(c(1,1),2,1)
  i=sample(1:nrow(x_data),1)
  diff=x_data[i,]%*%theta-y_data[i,]
  gradient=(x_data[i,])%*%diff
  while (!((abs(gradient[1,1])<1e-5)&(abs(gradient[2,1])<1e-5))){
    theta=theta-learning_rate*gradient
    j=sample(1:nrow(x_data),1)
    diff=x_data[j,]%*%theta-y_data[j,]
    gradient=(x_data[j,])%*%diff
  }
  func=paste('y=',theta[1,1],'+',theta[2,1],'x')
  return (func)
}
```


